Homicide Increases in the COVID-19 Era

### 2025-02-25 Draft1.qmd
added ggplot ideas

@@

@@

* histogram (we did a barplot)
* boxplots!
* geom_tile - correlations
*

@@

## Figure 4 - Gender Distribution for crimes over time {.unnumbered}

>>>>

# Combine the two datasets
crime_la <- rbind(crime_la_2010_2019, crime_la_2020_present)
```

```{r}
# Secondary dataset - Median Income by ZCTA
california_median_income_2018_2023 <- list()
yrs <- 2018:2023
for (i in 1:length(yrs)) {
  obj <- read.csv(paste0("Raw_Data/ACSST5Y",yrs[[i]],".S1903-Data.csv"), skip = 0)
  obj <- obj[-1,]
  obj$year <- yrs[[i]]
  california_median_income_2018_2023[[i]] <- obj
}

@@

```{r}
# Secondary dataset - COVID cases in Los Angeles County
covid_14day <- read.csv("Raw_Data/LA_County_Covid19_CSA_14day_case_death_table.csv")

covid_la <- covid_14day %>% filter(grepl("Los Angeles", geo_merge))
covid_la$area <- gsub("Los Angeles - ", "", covid_la$geo_merge)
```

@@

* histogram (we did a barplot)
* boxplots! - 
* geom_tile - correlations - Bianca
* geom_jitter

@@

# Figure 4 - Gender Distribution for crimes over time {.unnumbered}
